### 2025-07-03 paper/sections/other/main_results.qmd
now done

@@

df = final_table(res_dir)
inputs = get_table_inputs(df, nothing; backend=Val(:latex))
formatters = (
    PrettyTables.ft_round(1,findall(.!contains.(names(df),"Acc"))),
    PrettyTables.ft_round(2,findall(contains.(names(df),"Acc")))
)
for fname in ["paper/quarto_ecml/tables/main.tex","paper/preprint/tables/main.tex"]
    tabulate_results(
        inputs; 
        table_type=:tabular, 
        save_name=fname, 
        wrap_table=false, 
        alignment=[:l,fill(:r,size(df,2)-1)...],
        formatters=formatters
    )
end
```

>>>>

## Final Results {#sec-app-final-results}

Plus/minus two standard deviations of bootstrap estimates.

<!-- Standard deviation of bootstrap is the standard error. -->

@@

df = final_table(res_dir)
inputs = get_table_inputs(df, nothing; backend=Val(:latex))
formatters = (
    PrettyTables.ft_round(1,findall(.!contains.(names(df),"Acc"))),
    PrettyTables.ft_round(2,findall(contains.(names(df),"Acc")))
)
for fname in ["paper/quarto_aaai/tables/main.tex","paper/preprint/tables/main.tex"]
    tabulate_results(
        inputs; 
        table_type=:tabular, 
        save_name=fname, 
        wrap_table=false, 
        alignment=[:l,fill(:r,size(df,2)-1)...],
        formatters=formatters
    )
end
```

# Standard errors with hyperparameter uncertainty marginalized out:
df = final_table(res_dir, total_uncertainty=true)
inputs = get_table_inputs(df, nothing; backend=Val(:latex))
formatters = (
    PrettyTables.ft_round(1,findall(.!contains.(names(df),"Acc"))),
    PrettyTables.ft_round(2,findall(contains.(names(df),"Acc")))
)
for fname in ["paper/quarto_aaai/tables/main_total.tex","paper/preprint/tables/main_total.tex"]
    tabulate_results(
        inputs; 
        table_type=:tabular, 
        save_name=fname, 
        wrap_table=false, 
        alignment=[:l,fill(:r,size(df,2)-1)...],
        formatters=formatters
    )
end
```
